### 2022-08-23 article.tex
Remove figures
Quote Linus

Here we define paradata as the data that describes the process of generating data.
In genetic epidemiology, the data generated is mostly the results 
of an analysis (e.g. predicting a person having a disease),
as done by computer code.
In such context, one could argue incorrectly that
it is the scientific paper describes what the computer code does.
However, this has the unrealistic 
assumption that there is a perfect match between the paper and the code.
In this chapter it is argued that the source code should should be supplied,
as this is the true paradata: if the paper and code disagree, it is the
code that has generated the results.
The chapter concludes by some rules how to better code to serve as paradata,
and hence allowing computational research to be truly reproducible.

@@

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{Karesuando_church.jpg}
  \caption{
    Picture of Karesuando's church,
    the village where the Northern Swedish Population
    Health Study started.
    From \cite{hopfner2005}
  }
  \label{fig:karesuando_church}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{1189px-Eukaryote_DNA-en.png}
  \caption{
    A cell has a nucleus that contains chromosomes. 
    Each of these chromosomes (46 in humans) consist out of DNA. 
    DNA itself conists out of 4 nucleotides, 
    as depicted by the horizontal sticks 
    with the colors red, yellow, green and blue.
    From \cite{sponk2012}
  }
  \label{fig:eukakyote_dna}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{DNA_to_protein.png}
  \caption{
    Parts of DNA (so-called 'genes') code for proteins. 
    The DNA, that always stays put in the cell's nucleus, 
    is transcripted to messenger RNA (mRNA).
    mRNA leaves the nucleus and its code gets translated to 
    a protein sequence.
    Near the start of a gene are regions that determine the amount
    of proteins produced (not shown in figure).
    Adapted from \cite{shafee2015}
  }
  \label{fig:dna_to_protein}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{ahsan2017relative_table_2_sub.png}
  \caption{
    An example result of a genetic epideological research.
    It shows that the SNP named rs12133641 (located at position 154,428,283
    of chromosome 1) is highly correlated (p value is 3.0 * 10e-73, 
    961 individuals) to the concentration of the protein IL6RA, as measured
    in blood. The table is a simplified result from \cite{ahsan2017relative}.
  }
  \label{fig:ahsan2017relative_table_2_sub}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{ahsan2017relative_s6.png}
  \caption{
    The relation between the genotype for SNP rs12133641 
    and the protein concentration of IL6RA is relatively strong.
    The X axis shows the the genotype of the individuals,
    where 0 denotes AA, 1.0 denotes AG and 2.0 denotes GG.
    The Y axis shows the concentration of the protein IL6RA 
    as found in the participants' blood. n = 1 denotes the number
    of SNPs that were determined to be involved.
  }
  \label{fig:ahsan2017relative_s6}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{peng2011reproducible_fig_1.png}
  \caption{
    Levels of reproducibility, from \cite{peng2011reproducible}
  }
  \label{fig:peng2011reproducible}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{baggerly2009deriving_fig_1a.png}
  \caption{
    Gene expression result due to an off-by-one error.
    The cells in the main table show how much mRNA is produced per cell 
    line (the columns) for different proteins (the rows).
    The colors above the cells, with the dendrogram, shows
    red for cells that do not respond (red) and do respond (blue) to an 
    antibiotic.
    The purple rectangles show samples that are duplicated.
    Note that, due to this, some
    samples that behave identically are both non-responders and responders.
    From \cite{baggerly2009deriving}
  }
  \label{fig:baggerly2009deriving}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{bbbq_article_issue_157.png}
  \caption{
    A typical GitHub repository (\cite{bbbqarticleissue157}), 
    hosting the code for a
    computational experiment, 
    as published with \cite{bilderbeek2022transmembrane}.
    Note that this repository has 72 commits, where a commit is a change
    to the code.
  }
  \label{fig:bbbqarticleissue157}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{build_badge.png}
  \caption{
    A build badge for the GitHub repository of this article.
    The description indicates which process it is that the badge
    signals success (as in this case) or failure of. 
  }
  \label{fig:build_badge}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[]{badge_codecov.png}
  \caption{
    A build badge for the code coverage of an R 
    package (\url{https://github.com/ropensci/beautier}).
    The umbrella signals that the code coverage is hosted by
    CodeCov (\url{https://codecov.io/}). 
    The text indicates which process it is that the badge
    signals, which in this case, is that the code is fully covered
    by tests.
  }
  \label{fig:badge_codecov}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{daisie_contributors.png}
  \caption{
    An overview of the commits that multiple contributors have
    made, in this case, to the code of DAISIE (\cite{etienne2020daisie})
  }
  \label{fig:daisie_contributors}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{issue_ldpred2.png}
  \caption{
    An overview of the issues for the code for
    LDpred2 (\cite{prive2020ldpred2}). Of the 310 issues, 300 have been closed.
    The first four issues have been replied to, as indicated by the
    talk balloon. The fifth issues has a label with the text 'feature request'
    to signal the issue type.
  }
  \label{fig:issue_ldpred2}
\end{figure}

@@

% \paragraph{A paper contains data and should be FAIR data}

A paper contains and/or describes data, where we define
data as 'individual facts, statistics, or items of information, often 
numeric' \cite{glossary2003oecd}.
To ensure unhampered knowledge growth, this data should [TODO: Why? Reference!] 
follow the FAIR 
principles.
The FAIR principles \cite{wilkinson2016fair} are that data should be 
[TODO: there are probably better examples]
Findable (e.g. found by web),
Accessible (e.g. DataDryad and or Zenodo), 
Interoperable (e.g. plain-text file format, such as comma-separated files) 
and Reusable (e.g. work on all operating systems)

% \paragraph{A paper is data and should be FAIR data}

A paper in itself is data, as it is a collection of text and
figures that we itself can do measurements upon.
Also here, a paper should be FAIR, 
[TODO: there are probably better examples]
i.e.
Findable (e.g. having a DOI)
Accessible (e.g. open access publications, i.e. published in a public access
repository), 
Interoperable (e.g. written in English (i.e. the current lingua franca of sciece))
and Reusable (e.g. it is valid to cite and build upon earlier academic papers, 
it is peer-reviewed (i.e. satifies a minimal requirement of quality)).
This paper itself will later specify the standpoint that a paper
is metadata (i.e. data about data), instead of paradata (i.e.
data that describes the collection of data)

>>>>

Here we define paradata as the data that describes the process of generating data.
In genetic epidemiology, the data generated is mostly the results 
of an analysis (e.g. predicting a person having a disease),
as done by computer code.
In such context, one could argue incorrectly that
it is the scientific paper describes which computation steps 
have taken place.
However, this has the unrealistic 
assumption that there is a perfect match between the paper and the code.
In this chapter it is argued that the source code should should be supplied,
as this is the true paradata: if the paper and code disagree, it is the
code that has generated the results.
The chapter concludes by some rules how to better code to serve as paradata,
and hence allowing computational research to be truly reproducible.

@@

\epigraph{
  Talk is cheap. Show me the code. \\
  \\
  Linus Torvalds, 2000-08-25. Message to linux-kernel mailing list
}

@@

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{Karesuando_church.jpg}
  \caption{
    Picture of Karesuando's church,
    the village where the Northern Swedish Population
    Health Study started.
    From \cite{hopfner2005}
  }
  \label{fig:karesuando_church}
\end{figure}
\fi

@@

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{1189px-Eukaryote_DNA-en.png}
  \caption{
    A cell has a nucleus that contains chromosomes. 
    Each of these chromosomes (46 in humans) consist out of DNA. 
    DNA itself conists out of 4 nucleotides, 
    as depicted by the horizontal sticks 
    with the colors red, yellow, green and blue.
    From \cite{sponk2012}
  }
  \label{fig:eukakyote_dna}
\end{figure}
\fi

@@

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{DNA_to_protein.png}
  \caption{
    Parts of DNA (so-called 'genes') code for proteins. 
    The DNA, that always stays put in the cell's nucleus, 
    is transcripted to messenger RNA (mRNA).
    mRNA leaves the nucleus and its code gets translated to 
    a protein sequence.
    Near the start of a gene are regions that determine the amount
    of proteins produced (not shown in figure).
    Adapted from \cite{shafee2015}
  }
  \label{fig:dna_to_protein}
\end{figure}
\fi

@@

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{ahsan2017relative_table_2_sub.png}
  \caption{
    An example result of a genetic epideological research.
    It shows that the SNP named rs12133641 (located at position 154,428,283
    of chromosome 1) is highly correlated (p value is 3.0 * 10e-73, 
    961 individuals) to the concentration of the protein IL6RA, as measured
    in blood. The table is a simplified result from \cite{ahsan2017relative}.
  }
  \label{fig:ahsan2017relative_table_2_sub}
\end{figure}
\fi

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{ahsan2017relative_s6.png}
  \caption{
    The relation between the genotype for SNP rs12133641 
    and the protein concentration of IL6RA is relatively strong.
    The X axis shows the the genotype of the individuals,
    where 0 denotes AA, 1.0 denotes AG and 2.0 denotes GG.
    The Y axis shows the concentration of the protein IL6RA 
    as found in the participants' blood. n = 1 denotes the number
    of SNPs that were determined to be involved.
  }
  \label{fig:ahsan2017relative_s6}
\end{figure}
\fi

@@

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{peng2011reproducible_fig_1.png}
  \caption{
    Levels of reproducibility, from \cite{peng2011reproducible}
  }
  \label{fig:peng2011reproducible}
\end{figure}
\fi

@@

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{baggerly2009deriving_fig_1a.png}
  \caption{
    Gene expression result due to an off-by-one error.
    The cells in the main table show how much mRNA is produced per cell 
    line (the columns) for different proteins (the rows).
    The colors above the cells, with the dendrogram, shows
    red for cells that do not respond (red) and do respond (blue) to an 
    antibiotic.
    The purple rectangles show samples that are duplicated.
    Note that, due to this, some
    samples that behave identically are both non-responders and responders.
    From \cite{baggerly2009deriving}
  }
  \label{fig:baggerly2009deriving}
\end{figure}
\fi

@@

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{bbbq_article_issue_157.png}
  \caption{
    A typical GitHub repository (\cite{bbbqarticleissue157}), 
    hosting the code for a
    computational experiment, 
    as published with \cite{bilderbeek2022transmembrane}.
    Note that this repository has 72 commits, where a commit is a change
    to the code.
  }
  \label{fig:bbbqarticleissue157}
\end{figure}
\fi

@@

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{build_badge.png}
  \caption{
    A build badge for the GitHub repository of this article.
    The description indicates which process it is that the badge
    signals success (as in this case) or failure of. 
  }
  \label{fig:build_badge}
\end{figure}
\fi

@@

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[]{badge_codecov.png}
  \caption{
    A build badge for the code coverage of an R 
    package (\url{https://github.com/ropensci/beautier}).
    The umbrella signals that the code coverage is hosted by
    CodeCov (\url{https://codecov.io/}). 
    The text indicates which process it is that the badge
    signals, which in this case, is that the code is fully covered
    by tests.
  }
  \label{fig:badge_codecov}
\end{figure}
\fi

@@

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{daisie_contributors.png}
  \caption{
    An overview of the commits that multiple contributors have
    made, in this case, to the code of DAISIE (\cite{etienne2020daisie})
  }
  \label{fig:daisie_contributors}
\end{figure}
\fi

@@

\iffalse
\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\linewidth]{issue_ldpred2.png}
  \caption{
    An overview of the issues for the code for
    LDpred2 (\cite{prive2020ldpred2}). Of the 310 issues, 300 have been closed.
    The first four issues have been replied to, as indicated by the
    talk balloon. The fifth issues has a label with the text 'feature request'
    to signal the issue type.
  }
  \label{fig:issue_ldpred2}
\end{figure}
\fi

@@
